### 2021-06-16 paper/appendix_data.tex
Red texts -> comments, except for some ldots in figurenotes.
Move estimated parameters to model section. Address some comments.

\subsection{The Synthetic Population}

\textcolor{red}{\ldots}

@@

\textcolor{red}{Arbeitsplots auch in eine gemeinsame Graphik packen}

@@

\subsection{Infection Probabilities\comment[id=HM]{Is the data section the right place?}}
\label{subsec:infection_probs}

To calibrate infection probabilities outside of the model, it would be important to know
the exact duration and distance of each contact type as well as viral loads. Since this
is not available in any data set, we estimate those parameters inside the model with the
method of simulated moments \citep{McFadden1989} by minimizing the distance between
simulated and observed infection rates. Since our model includes a lot of randomness, we
average simulated infection rates over several model runs.

We use data for Germany from October 2020 until June 2021. We do not use
earlier periods for three reasons. Firstly, in the beginning PCR tests were highly
limited and therefore it would be difficult to find good initial conditions for our
simulations. In addition during the summer the case numbers were extremely low. This
could lead to the epidemic going extinct in our simulation. Additionally, our model does
not include international travel or other imports of cases. These would be important but
difficult to model during the summer months.

To avoid over-fitting and simplify the numerical optimization problem, we only allow for
five different probabilities: 1) for contacts in schools 2) contacts in preschools and
nurseries. 3) for work contacts. 4) for households. 5) for other contacts.

The infection probabilities estimated from our model are as follows: For household
contacts (each individual meets all his or her household members every day) the infection
probability is 10\%, for school contacts (all students and teachers meet all other
students and teachers that attend school that day and there are three classes taking
place each day) the probability of infection is 1.2\%, for preschools and nurseries that
infection probability is 0.5\%. Work contacts carry a risk of 14.5\% and other activities
(including leisure activities such as meeting friends) carry the highest risk with
15.875\%.\comment[id=HM]{Are these numbers current? In any case, a table would substitute for this and the previous paragraph. Need to mention B.1.1.7 alongside.}

@@

\subsection{Rapid Test Demand}

>>>>

\subsection{The Synthetic Population\comment[id=K]{To be written}}

@@

@@

@@

### 2021-06-16 paper/appendix_results.tex
Move estimated parameters to model section. Address some comments.

This compares simulated data from our model with empirical data from Germany. We look at
observed infections, fatality rates, the spread of the B117 mutation, vaccinations and
rapid test demands. Where available we do not only look at aggregated statistics but also
analyze the model fit for age groups.\comment[id=J]{summarize the fit; Some of this needs
to go in the appendix. I suggest the age group and federal state fit goes there???}

@@

\subsection{Share of Cases that are Detected}
\label{subsec:appendix_share_known_cases}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group in the Main Prediction}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textcolor{red}{\ldots}}
\end{figure}

It's noteworthy that the share of detected cases increases rapidly in May for the five to fourteen year olds. This is a direct result of the mandatory tests in school.\comment[id=K]{We don't do this at the moment but we could also create plots showing the share of detected cases between scenarios - either for the full population or for a age group of interest.}

\subsection{Rapid Tests}
\label{subsec:appendix_rapid_tests}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/demand_shares}
  \caption{Share of the Population Demanding a Rapid Test for a Particular Reason}
  \label{fig:rapid_tests_by_reason}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without PCR demand and other contact demand together form the private demand category. Also note that these do not add up to the total share of demanded rapid tests as individuals may have more than one reason to demand a rapid test on any given day. \textcolor{red}{\ldots}}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_demand}
  \caption{Share of Individuals that Demand a Rapid Test for a Particular Reason that are Actually Infected}
  \label{fig:share_of_rapid_tests_by_reason_by_infected}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without PCR demand and other contact demand together form the private demand category. Also note that this is not the same as individuals getting a positive rapid test. The sensitivity is quite low before individuals become infectious. Therefore, if individuals are still in the latent period of their infection they are likely to get a false positive rapid test. \textcolor{red}{\ldots}}
\end{figure}

>>>>

This compares simulated data from our model with empirical data from Germany. We look at
observed infections, fatality rates, the spread of the B117 mutation, vaccinations and
rapid test demands. Where available we do not only look at aggregated statistics but also
analyze the model fit for age groups.\comment[id=J]{summarize the
fit}\comment[id=HM]{Also need to show simulated total infections somewhere. So far only
ever shown for 2021.}

@@

\subsection{Share of Cases that are Detected  \comment[id=K]{Figure notes missing}}
\label{subsec:appendix_share_known_cases}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group in the Main Prediction}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent}
\end{figure}

It's noteworthy that the share of detected cases increases rapidly in May for the five to
fourteen year olds. This is a direct result of the mandatory tests in
school.

\subsection{Rapid Tests \comment[id=K]{The figures will likely change layout later}}
\label{subsec:appendix_rapid_tests}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/demand_shares}
  \caption{Share of the Population Demanding a Rapid Test for a Particular Reason}
  \label{fig:rapid_tests_by_reason}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without
  PCR demand and other contact demand together form the private demand category. Also
  note that these do not add up to the total share of demanded rapid tests as individuals
  may have more than one reason to demand a rapid test on any given day. }
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[width=\textwidth]{../figures/results/figures/rapid_test_statistics/share_infected_among_demand}
  \caption{Share of Individuals that Demand a Rapid Test for a Particular Reason that are Actually Infected}
  \label{fig:share_of_rapid_tests_by_reason_by_infected}
  \floatfoot{\noindent Note that the lower three (household demand, symptomatic without
  PCR demand and other contact demand together form the private demand category. Also
  note that this is not the same as individuals getting a positive rapid test. The
  sensitivity is quite low before individuals become infectious. Therefore, if
  individuals are still in the latent period of their infection they are likely to get a
  false positive rapid test.}
\end{figure}

### 2021-06-16 paper/report.tex
Move estimated parameters to model section. Address some comments.

Since early 2020,\comment[id=J]{\textbf{Features that are not highlighted enough:}

\begin{itemize}
    \item Low sensitivity of rapid tests before and on day of infectiousness onset
    \item Different seasonalities for different contact types (and quite strong for other contacts)
    \item Low number of breakpoints in parameters / policies compared to breakpoints in
    cases / reproduction rate
\end{itemize}

} the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=HM]{Need to find some more scientific citation
before submission} In the meantime, it is of utmost importance to employ an effective
mix of strategies for containing the virus. The most frequent initial response was a set
of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While
this has allowed some countries to sustain equilibria with very low infection
numbers\footnote{See \citet{Contreras2021} for a theoretical equilibrium at low case
numbers which is sustained with test-trace-and-isolate policies.}, most have seen large
fluctuations of infection rates over time. Containment measures have become increasingly
diverse and now include testing, more nuanced NPIs, and contact tracing. Neither these
policies' effect nor the influence of seasonal patterns or more infectious virus strains
are well understood in quantitative terms.

@@

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed and there are aggregate capacity constraints throughout. In
contrast, rapid antigen tests yield immediate results; after a phase-in period, all
tests that are demanded will be performed. Specificity and sensitivity of these tests is
set according to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on
the timing of the test relative to the start of infectiousness.
Figure~\ref{fig:antigen_tests} shows our model for rapid test demand. Schools may
require students to be tested regularly. Rapid tests may be offered by employers for
on-site workers. Individuals may demand tests for private reasons, which include having
plans to meet other people\footnote{A positive test will make them reduce their
contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons and whether she reduces her contacts if
she tests positive or develops symptoms. The thresholds are higher for tests in a
private setting than for tests at the workplace until mid April and then compliance
because of private reasons becomes higher than compliance at the
workplace.\comment[id=J]{Shouldn't we mention that this is because of availability /
high costs?}

@@

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that age-specific
simulated infections predict the corresponding time series in the data \citep[see][for
the general method]{McFadden1989}. However, the two sets of time series are not
comparable directly because not all cases will be recorded. We thus model recorded cases
as depicted in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of
the share of recorded cases and use data on whether CoViD-19 symptoms led to a PCR test
in order to get age-specific shares. For example,\comment[id=HM]{@Janos, please correct
if necessary and insert reference} estimate unknown cases to be twice as high for
children as for adults. Confirmation of a positive rapid test result is another reason
for PCR tests, once these become available.\comment[id=J]{Free parameters also include:

- One hygiene multiplier for school an work contacts after November 2
- A few "other" multipliers including two lockdown fatigue effects
- Number of extra contacts during holidays

Strictly speaking also:
- The fade in speed of the rapid tests
- Share known cases around holidays }

@@

We draw simulated samples of agents from the distribution of recorded infections in
September 2020 and use the model to predict recorded infection rates until the end of May
2021.\comment[id=J]{I do not understand} See Supplementary
Materials~\ref{sec:data_and_parameters} and \ref{sec:model} for detailed descriptions of
the data and the model, respectively. The blue line in Figure~\ref{fig:aggregated_fit}
shows our model's predictions are very close to officially recorded cases in the
aggregate. This is also true for infections by age and geographical region, which are
shown in the supplementary materials (Figures~\ref{fig:age_group_fit} and
\ref{fig:state_fit}, respectively).

>>>>

Since early 2020,\comment[id=J]{Put stronger focus on time dependent rapid test
sensitivity (30\% before day of onset of infectiousness)} the CoViD-19 pandemic has
presented an enormous challenge to humanity on many dimensions. The development of highly
effective vaccines holds the promise of containment in the medium term. However, most
countries find themselves many months---and often years---away from reaching
vaccination-induced herd immunity \citep{Swaminathan2021}.\comment[id=HM]{Need to find
some more scientific citation before submission} In the meantime, it is of utmost
importance to employ an effective mix of strategies for containing the virus. The most
frequent initial response was a set of non-pharmaceutical interventions (NPIs) to reduce
contacts between individuals. While this has allowed some countries to sustain equilibria
with very low infection numbers\footnote{See \citet{Contreras2021} for a theoretical
equilibrium at low case numbers which is sustained with test-trace-and-isolate
policies.}, most have seen large fluctuations of infection rates over time. Containment
measures have become increasingly diverse and now include testing, more nuanced NPIs, and
contact tracing. Neither these policies' effect nor the influence of seasonal patterns or
more infectious virus strains are well understood in quantitative terms.

@@

We include two types of tests. Polymerase chain reaction (PCR) tests reveal whether an
individual is infected or not; there is no uncertainty to the result. PCR tests require
some days to be processed and there are aggregate capacity constraints throughout. In
contrast, rapid antigen tests yield immediate results; after a phase-in period, all tests
that are demanded will be performed. Specificity and sensitivity of these tests is set
according to data analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the
timing of the test relative to the start of infectiousness.
Figure~\ref{fig:antigen_tests} shows our model for rapid test demand. Schools may require
students to be tested regularly. Rapid tests may be offered by employers for on-site
workers. Individuals may demand tests for private reasons, which include having plans to
meet other people\footnote{A positive test will make them reduce their contacts; this is
why tests impact the actual contacts in Figure~\ref{fig:model-description}.}, showing
symptoms of CoViD-19, and because a household member tested positively for the virus. We
endow each agent with an individual compliance parameter. This parameter determines
whether she takes up rapid tests offered by employers or follows up on private reasons
and whether she reduces her contacts if she tests positive or develops symptoms. The
thresholds fall over time and are calibrated to survey data where possible (see
Supplementary Materials~\ref{subsec:rapid_test_demand}).
% The thresholds are higher for tests in a private setting than for tests at the
% workplace until mid April and then compliance because of private reasons becomes higher
% than compliance at the workplace.

@@

The free parameters are the infection probabilities by contact category, one hygiene
multiplier for school and work contacts after November 2nd 2020, approx. ten parameters
that govern the reduction of other contacts\comment[id=K]{Must be updated when the
estimation is finished.}, the number of extra contacts during holidays, the share of
detected cases around holidays and the fade in speed of the rapid tests as well as one
parameter that governs the import of B.1.1.7 cases in January 2021. For details, see
Supplementary Material~\ref{subsec:estimated_params},~\ref{subsec:rapid_test_demand}.

We estimate these parameters such that the model matches the following empirical
quantities: 1. official case numbers for each age group and region, 2. deaths, 3. share
of B.1.1.7. \citep[See][for the general method]{McFadden1989}. However, only a fraction
of infections actually enter the official case numbers. We thus model official cases as
depicted in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of the
share of detected cases and use data on whether CoViD-19 symptoms led to a PCR test. As
the share of asymptomatic individuals varies by age group, this gives us age-specific
shares (see Figure~\ref{fig:share_known_cases_by_age_group} for the share of known cases
by age group over time in our model). Our estimates suggest that only 18 to 28\% of cases
are detected for school age children while the rate is 30 to 55\% for those above age
80.\comment[id=K]{Must be verified once results are final.} Confirmation of a positive
rapid test result is another reason for PCR tests, once these become available.

@@

We draw simulated samples of agents from the distribution of recorded infections in
September 2020 and use the model to predict recorded infection rates until the end of May
2021.\comment[id=J]{This needs more explanation. I will rewrite this.} See Supplementary
Materials~\ref{sec:data_and_parameters} and \ref{sec:model} for detailed descriptions of
the data and the model, respectively. The blue line in Figure~\ref{fig:aggregated_fit}
shows our model's predictions are very close to officially recorded cases in the
aggregate. This is also true for infections by age and geographical region, which are
shown in the supplementary materials (Figures~\ref{fig:age_group_fit} and
\ref{fig:state_fit}, respectively).
